\documentclass{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}


\begin{document}

\part{Giacomo Romanini}


\section{Education}

\begin{eventlist}

      \item{2022-July 2025}
            {Università di Bologna, highest mark in}
            {Master in Computer Engineering}

      - \underline{Scalable and Reliable Services}:
            best practices and approaches over cloud technologies. 
            Project to design a scalable architecture on Azure

      - \underline{Software Systems Engineering}: 
            analysis and development organized in sprints.

      - \underline{Processors}: pipeline and out-of-order execution on modern processors. 

      \textbf{Erasmus} at Vilnius' VGTU:

      - \underline{Intelligent Systems}: FNN, training and backpropagation.

      - \underline{Iot}: project involving microcontrollers and server communication for low energy systems.

      \item{2018-2022}
            {Università di Bologna}
            {Bachelor in Computer Engineering}

      - \underline{Software Engineering}:
            requirements, use cases and risk analysis to define the problem and create the architectural model. 
            Definition of ER domain, class structure, and test cases.
            
      - \underline{Operating Systems}:
            coordination of processes and tasks in a time and memory sensitive environment.

      \item{2013-2018}
            {Liceo Ettore Majorana, San Lazzaro di Savena (BO)}
            {High School of Applied Sciences}

            Scientific specialization with programming lessons
\end{eventlist}

\section{Work Experience}

\begin{eventlist}

      \item{Mar 2021 - Feb 2024}
            {Luna Srl, Bologna}
            {Junior Developer}

      - Developed programs and applications, defining processes flows and use cases.\newline
      - Maintenance of a web-browser management app. 
      Resolved issues with orphaned many-to-many relationships and deleted references.
      Reduced by 66.7\% the initial loading time,
      and halved some data retrieval time by optimizing SQL queries.

      \item{Apr 2017 - July 2017}
            {123FATTO, Pianoro}
            {Technical Support}

      Hardware and Software analysis and testing to build, repair and optimize clients' computer. \newline
      Store management and clients relations.
      
      %\noindent\hfil\rule{0.3\textwidth}{.4pt}
      \item{May 2016 - June 2016}
            {ANT Italia, Bologna}
            {Internal Technical Support}

      Hardware and Software maintenance and support, collaborating with technicians and associates to solve office stations' and server's problems.
\end{eventlist}



\personal
[https://github.com/RedDuality/]
{Via Adriano Colombo 71, 40065, Pianoro (BO), Italy}
{g.romanini2@gmail.com}
{}

\section{Projects}

\begin{yearlist}
  \item {Active}
        {WYD (\href{https://wyd-63r.pages.dev}{Website})}
        {Scalable event-sharing app with automatic media retrieval.
              \newline
              \textbf{Front End (\href{https://github.com/RedDuality/WYD}{GitHub})}
              \newline
              Flutter interface for sharing and confirming events, 
              with automatic media retrieval from the device and real-time/long-polling updates.
              \newline
              \textbf{Back End (\href{https://github.com/RedDuality/WYD_Server}{GitHub})}
              \newline
              Stateless REST server with sharded MongoDB, MinIO object storage and message queue for update propagation.}
  \item {2025}
        {B. Future Challenge}
        {Collaborated in an interdisciplinary team to design a concept AI-driven analytics assistant, 
        developing the data infrastructure.}
  \item {2024}
        {Forward for Snitch (\href{https://github.com/RedDuality/snitch_forward}{GitHub})}
        {Parallelized LLaMA 2’s forward function on a RISC-V 8-core Spike CPU.}
  \item {2023}
        {Intelligent Systems (\href{https://github.com/RedDuality/IntelligentSystems}{GitHub})}
        {Designed and trained neural networks for intelligent system applications.}
  \item {2023}
        {Virtual-Robot (\href{https://github.com/RedDuality/issLab23}{GitHub})}
        {Developed an actor-based software engineering project simulating robotic behaviors.}
  \item {2021}
        {Farmabyte (\href{https://github.com/lorenzo9uerra/farmabyte-doc}{GitHub})}
        {Conducted problem analysis and implemented solutions in a software engineering project.}
\end{yearlist}

\section{Skills}

\begin{factlist}
      \item {Technical}
            {Java, Spring, C\#, C, Go, Angular, Flutter, React, SQL, MongoDB, git, Docker, Arduino, MATLAB}\\
      \item {Organiz.}
            {Agile, Process Design, Strategy Dev., Nonviolent Communication, Coordination}\\

      \item {Learning}
            {Security, DevOps, Kubernetes, game development, photo editing}\\

      \item {Additional}
            {Italian C2, English C1, Category B driving licence (Italy), Scout leader, Guitar}\\
            
\end{factlist}

\privacyDisclaimer

\end{document}